\documentclass{article}
\begin{document}
This is my \emph{first} document prepared in \LaTeX.

\noindent We have seen that to typeset something in \LaTeX, we type in the text to be typeseet together with some \LaTeX\ commands. Words must be sepearted by
spaces (does not matter how many) and lines maybe broken arbitrarily.

\noindent The end of a paragraph is specified by a \emph{blank line} in the input. In other words, whenever you want to start a new paragraph, just leave a blank
line and proceed.

\noindent Carrots are good for your eyes, since they contain Vitamin A\@. Have you ever seen a rabbit wearing glasses?

\noindent The numbers 1, 2, 3, etc.\ are called natural numbers. According to Kronecker, they were made by God; all else being the works of Man.

\noindent I think \LaTeX is fun.

\noindent I think \LaTeX\ is fun.

Note the difference in right and left quotes in 'single quotes' and ''double quotes'''.

Note the difference in right and left quotes in `single quotes' and 	``double quotes''.

Note the difference in right and left quotes in \lq single quotes\rq\ and \lq\lq double quotes\rq\rq.

X-rays are discussed in pages 221--225 of Volume 3---the volume on the electromagnetic waves.

\'{E}l est\'{a} aqu\'{\i}

Maybe I have now learnt about 1% of \LaTeX.


Maybe I have now learnt about 1\% of \LaTeX.

\textasciitilde \#  \$  \% \textasciicircum \& \_ \textbackslash \{ \} 

\noindent This is the first line. \\ This is the second line.

\noindent This is the first line.\\ [10pt] This is the second line.

\begin{center}
The \TeX nical Institute \\[.75cm]
Certificate
\end{center}
\noindent This is to certify that Mr. N. O. Vice has undergone a course that this institute and is qualified to be a \TeX nician.
\begin{flushright}
The Director\\ The \TeX nical Institute
\end{flushright}

\begin{flushleft}
The Director\\ The \TeX nical Institute
\end{flushleft}

\noindent \textsf{\textbf{sans serif family, boldface series, upright shape}} \\
\textrm{\textsl{roman family, medium series, slanted shape}} \\
\textrm{roman}
\textsf{sans serif}
\texttt{typewriter}
\textmd{medium}
\textbf{boldface}
\textup{upright}
\textit{italic}
\textsl{slanted}
\textsc{small cap}

\textbf{A polygon of three sides is called a \emph{triangle} and a polygon of four sides is called a \emph{quadrilateral}}

By a {\bfseries triangle}, we mean a polygon of three sides.

{\upshape upright} {\itshape italic} {\slshape slanted} {\scshape small cap} {\mdseries medium} {\bfseries boldface} {\rmfamily roman} {\sffamily sans serif}
{\ttfamily typewriter} 

{\large size} {\Large size} {\LARGE size} {\huge size} {\Huge size}

{\tiny size} {\scriptsize size} {\footnotesize size} {\small size} {\normalsize size}

\begin{center}
{\bfseries\huge The \TeX nical Institute}\\[1cm]
{\scshape\LARGE Certificate}
\end{center}

\noindent This is to certify that Mr. N. O. Vice has undergoe a course at this institute and is qualified to be a \TeX nical Expert.

\begin{flushright}
{\sffamily The Director\\ The \TeX nical Institiute}
\end{flushright}
\end{document}
